---
title: "TAR simulation (constant threshold)"
author: "Shota Komatsu"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
library(magrittr)
library(ggplot2)
library(foreach)
# Load a function that estimates TAR parameters.
source("../R/TAR_with_constant_threshold.R")
```

# Setting parameters

```{r}
# Set seed
set.seed(123)
# Number of observations + 1
n <- 5001
# Draw data from normal distribution
y <- rnorm(n, mean = 0, sd = 10)
z <- rep(0, n)
e <- rnorm(n, mean = 0, sd = 5)
# AR parameter
rho <- -0.5
# Threshold value
theta <- 10
```

# Simulating data

We will simulate the data folling the data generating process below:

$$
\begin{align}
&m_{t} - m_{t-1} = \rho m_{t-1} \times 1 \{\lvert m_{t-1} \rvert > \theta  \} + \varepsilon_{t} \\
\Leftrightarrow \quad &m_{t} = (1 + \rho) m_{t-1} \times 1 \{\lvert m_{t-1} \rvert > \theta  \} + \varepsilon_{t},
\end{align}
$$
where $m_{t} := y_{t} - y_{t-1}$.

```{r}
# Make dataset
df <- tibble::tibble(y, z, e) %>%
  dplyr::mutate(L.y = dplyr::lag(y, k = 1)) %>%
  dplyr::mutate(m = y - L.y) %>%
  dplyr::mutate(t = 0:(n-1)) %>%
  dplyr::filter(!is.na(m))

for (i in 2:nrow(df)) {
  if (abs(df$m[i-1]) <= theta) {
    df$m[i] <- df$m[i-1] + df$e[i]
    df$z[i] <- 0
  }
  else if (df$m[i-1] < -theta) {
    df$m[i] <- (1 + rho) * df$m[i-1] + df$e[i]
    df$z[i] <- -1
  }
  else {
    df$m[i] <- (1 + rho) * df$m[i-1] + df$e[i]
    df$z[i] <- 1
  }
}
```


```{r}
# Plot the simulated data
ggplot(data = df, aes(x = t, y = m)) + 
  geom_line()
```


- $z_{t} = 1$ if $m_{t-1} > \theta$.
- $z_{t} = 0$ if $- \theta \leq m_{t-1} \leq \theta$.
- $z_{t} = -1$ if $m_{t-1} < - \theta$.

```{r}
# Plot to which regime each observation belongs.
ggplot(data = df, aes(x = t, y = z)) + 
  geom_point(size = 1)
```

# Estimating the parameters

The estimation of TAR model consists of the following steps:

1. The possible candidates for $\theta$ are selected from the $m_{t}$ in the data in such a way that at least 20% of observations are either within or outside the band formed by the thresholds. This means that to assure regime switching, you exclude the candidates which make almost all $m_{t}$ inside or outside the band.

1. For each candidate $\theta$, create a variable $z_{t}$ that takes 1 if $\lvert m_{t-1} \rvert > \theta$ and 0 otherwise.

1. Compute $m_{t-1} \times z_{t}$.

1. Regress $m_{t} - m_{t-1}$ on $m_{t-1} \times z_{t}$. Compute the sum of squared residuals ($RSS(\theta)$).

1. Select the model that minimizes $RSS(\theta)$.

The absolute value of $\rho$ measures the adjustment speed. In the literature of market integration with the autoregressive approach, it is conventional to report ‘halflife’ values to show how fast markets respond to arbitrage opportunities. A halflife value $h$ is defined by
$$
h := \frac{\ln(0.5)}{\ln(1 + \rho)},
$$
which measures how much time is needed for a given shock to return to half its initial value. The smaller $h$ is, the faster the adjustment is.


```{r}
# Estimation
result1 <- TAR_const(df$m)
theta1 <- round(result1$theta, digits = 3)
halflife1 <- round(result1$halflife, digits = 3)
# Regression table
stargazer::stargazer(
  result1$regression, 
  type = "text", 
  add.lines = list(c("Threshold Value", theta1), c("Halflife", halflife1))
)
```

Check if RSS is minimized around the true parameter.

```{r}
plot(result1$rssplot + ggplot2::geom_vline(xintercept = theta, linetype = "dotted"))
```

Compare the true and estimated parameters.

```{r}
# Compare the true and estimated parameters
comparison <- 
  data.frame(
    parameter = c("rho", "theta"),
    true = c(rho, theta),
    estimate = c(as.numeric(result1$regression$coefficients), theta1)
  )
comparison
```

